%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Sr. Software Engineer (Android)} % Job title
    {Mobile Apps Team, ACI Ltd.} % Organization
    {Tejgaon, Dhaka, Bangladesh} % Location
    {Oct. 2017 - Present } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked as part of a team to completely organize and architect the two Educational Android App to implement a newer UI and improved performance.}
         \item {Project management using Jira, scrum, and Agile methodologies \& contributed to full life cycle development of applications.}
        \item {Individually implemented multiple new features including 'Push Notifications', 'media player', 'quiz', 'Java game development, and more.}
        \item {Solely responsible for integrating different libraries, implementing API endpoints, localization of strings, and more.}
        \item {Implemented several API microservices in Node.js, socket.io, and Java Animation based logical games.}
        \item {Worked on more than 50 projects \& responsible for resolving bugs, production, and QA issues.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer \& Project Manager (Android+Web), \textbf{Part Time}} % Job title
    {Nobo IT} % Organization
    {Mirpur, Dhaka, Bangladesh} % Location
    {Jan. 2018 - Dec. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {As the only android developer for the company, very quickly jumped on board and took full responsibility of the development and operation of the app.}
        \item {Performed bug fixes on existing code and analyzed existing code to proactively detect and fix code. Performed an extensive code review to better understand the entire code.}
        \item {Developed 10+ different kinds of projects including Property Search, Educational \& Ecommerce app}
        \item {Responsible for resolving bugs, production and QA issues.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Sr. Software Engineer (Android)} % Job title
    {TiCON System Ltd} % Organization
    {Uttara, Dhaka, Bangladesh} % Location
    {Nov. 2016 - Sep. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Took bottom line responsibility for push notifications, using Javascripts to integrate with the Android app.}
        \item {Designed and developed background jobs to run at regular intervals to send alerts to users who have downloaded the app but have not made any progress in ‘n’ number of days.}
        \item {Implemented the receiver and extracted JSON messages from Push notifications to direct it to the target activity.}
        \item {Developed Audio-Video streaming app named Willfon, Miruphone \& others.}
        \item {Single-handed design and implementation of Admin module.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Android Engineer} % Job title
    {Invogue Software Limited} % Organization
    {Gulshan, Dhaka, Bangladesh} % Location
    {Jul. 2016 - Nov. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked individually as well as part of a larger team on developing and maintaining multiple client applications.}
        \item {Worked on multiple emulators and test deployment and interoperability on multiple platforms.}
        \item {Developed more than 15 projects including a Car buy-sell app named Peepep.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer (Android, Back End)} % Job title
    {Multiplexer Lab} % Organization
    {Agargaon, Dhaka, Bangladesh} % Location
    {Dec. 2015 - Jun. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed app doctor-patient consultant \& social photo-sharing app.}
        \item {Implemented overall Android application logic and wrote API server for service, with project lead engineer.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Junior Software Engineer} % Job title
    {Emporium Technology Ltd.} % Organization
    {Dhanmondi, Dhaka, Bangladesh} % Location
    {Jan. 2015 - Dec. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a game like flappy bird using Java.}
        \item {Developed apps like company profile, all newspaper reader \& more.}
        \item {Assist in the budget for internal hardware/software along with Developer, manage architecture diagrams/plans.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}