%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Educational and Learning application} % Role
    {Medhabir Supernova} % Event
    {Client: ACI Ltd} % Location
    {Nov. 2019 - Ongoing} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Medhabir Supernova is the Educational and learning application that aims to help the secondary (Class 6-10) level students in Bangladesh to enhance and develop their knowledge.}
        \item {It offers 325 instructional animated videos, chapter-wise pdf, beautifully highlighted summaries, and other learning contents. Several exercises, exams, model tests, and quiz will increase proficiency in every subject.}
        \item {The app will be published soon. \href{https://fir-rtdb-1654a.firebaseapp.com/apk/Medhabir_Supernova.apk}{App link: \underline{Medhabir Supernova}} }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Educational and Learning application} % Role
    {Kids Brain Builder} % Event
    {Client: ACI Ltd} % Location
    {Jun. 2021 - Ongoing} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Kids Brain Builder is the Educational and learning application that aims to help the kids to enhance and develop their basic knowledge.}
        \item {It offers 200 animated videos, 100 logical games, and other learning content. }
        \item {The app will be published soon. \href{https://fir-rtdb-1654a.firebaseapp.com/apk/Kids_Brain_Builder.apk}{App link: \underline{Kids Brain Builder}} }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

%---------------------------------------------------------
  \cventry
    {Property Search application} % Role
    {Waseka} % Event
    {Client: UK} % Location
    {Jan. 2020 - Dec. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Search residential, commercial properties for sale, letting agents in your area or by name across the UK}
        \item {Compare house prices with Waseka's house prices}
        \item {\href{https://play.google.com/store/apps/details?id=co.uk.waseka}{Play store link: \underline{Waseka}} }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

%---------------------------------------------------------
  \cventry
    {Islamic Educational application} % Role
    {Ahmadiyya Bangla Prokashona} % Event
    {Client: MKA Bangladesh} % Location
    {Feb. 2022 - Aug. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Learn Islamic education through Quran and other pdf books \& load web content through trusted web}
        \item {\href{https://play.google.com/store/apps/details?id=com.mkab.publications}{Play store link: \underline{Ahmadiyya Bangla Prokashona}} }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
